Towards completely caring 15-minute neighbourhoods

### 2025-01-30 paper/Manuscript.tex
R1 submitted.

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{unicode-math}
\usepackage{hyperref}
\def\tightlist{}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Towards completely caring 15-minute neighbourhoods},
  pdfauthor={Anastasia Soukhov; Léa Ravensbergen; Lucía Mejía Dorantes; Antonio Páez},
  pdfkeywords={Accessibility, Mobility of Care, Gender, 15-minute
neighbourhood, Care Complete Neighbourhoods},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    Accessibility \sep Mobility of Care \sep Gender \sep 15-minute
neighbourhood \sep 
    Care Complete Neighbourhoods
\end{keyword}
\end{frontmatter}

@@

The ``15-Minute City'' concept has been embraced by global leaders to
promote human-scale neighbourhoods with transport and land-use designs
that support short trips to daily necessities. This paper bridges the
15-Minute City to ``Mobility of Care'', a framework that foregrounds
travel to care destinations, travel done predominately by women. This
focus contrasts the more commonly studied travel to employment and
leisure destinations. While the 15-Minute City concept is flexible
enough to consider all destination types, gendered examinations are
relatively lacking in the literature, and little research to date has
focused explicitly on care destinations. This gap is addressed in this
paper by identifying which areas in the city of Hamilton, Canada are
`caring 15-minute neighbourhoods'. To do so, a database of care
destinations was compiled to estimate the number (using the cumulative
opportunity accessibility measure) and diversity of mix (using the
entropy measure) of care destinations within a 15-minute walk from
residential parcels. Using data-driven machine learning techniques
(Self-Organizing Maps and Decision Trees), neighborhoods were classified
into `caring 15-minute neighbourhood' typologies that are examined
across residential socio-economic profiles. Our results suggest that the
majority of caring 15-minute neighbourhoods are in the urban core, where
more lower-income households reside. In contrast, not caring 15-minute
neighbourhoods in higher-income peripheral areas. Areas that make good
candidates for urban policy intervention are identified, and the
implications of enhancing 15-minute walkable caring access are discussed
in relation to gender mainstreaming in transportation planning.

Keywords: 15-Minute City; 15-Minute Neighbourhoods; Chrono-Urbanism;
Accessibility; Mobility of Care; Cities of Proximity; Inequality; Gender
Gap

@@

From another perspective, feminist geographers, urban planners and other
researchers agree that urban structure influences travel, but city
planning falls short in planning for a neutral identity. In contrast,
cities ought to be planned according to the multiple identities of the
inhabitants
\citep{vacchelli_towards_2018, urbandevelopmentviennaGenderMainstreamingUrban2013}.
Researchers have demonstrated how mobility patterns differ according to
gender
\citep{lawWomenTransportNew1999, cresswell_gendered_2008, levy2013travel, little_gender_1994, tronto_toward_1990, neto_gender_2015}.
The causes for this are varied, and related to gendered social norms and
cultural factors that play a role in how, where, with whom, what for,
and how far we move. Women tend to travel shorter distances and more
frequently \citep{roorda_triap_2010, morency_distance_2011}, and conduct
more activities related to care no matter their stage of life
\citep{ilo_care_2018, garciaromanGenderDifferencesTime2022}. Combined,
these findings indicate that the spatial organization of activities has
a different impact according to gender, and therefore the 15-Minute City
concept should not be gender blind.

This work builds a theoretical bridge between the 15-Minute City and
Mobility of Care concepts to answer questions about what destinations
matter and who benefits from proximity planning. The Mobility of Care
term was coined in
\citet{sanchezdemadariagaMobilityCareIntroducing2013}; it refers to all
travel required to sustain the needs of a household, such as grocery
shopping, escorting children, travelling to health appointments, and
running errands. While decades of research have examined types of
household-serving trips (e.g., shopping trips, escorting to school),
\citet{sanchezdemadariagaMobilityCareIntroducing2013} was the first to
consider them all as one category. In doing so, care-related mobility
can be shown to comprise a significant proportion of daily travel,
characterizing approximately 30\% of adults' daily trips
\citep{sanchezdemadariagaMobilityCareIntroducing2013, sanchezdemadariagaMeasuringMobilitiesCare2019, ravensbergen2023exploratory}.
We argue that Mobility of Care is especially relevant to the 15-Minute
City, as care trips are necessary for \emph{all} people and they most
often occur at the local level. Moreover, care trips are of particular
gendered and socio-economic importance, as women, and especially those
within lower income households, complete the majority of care trips
\citep{ravensbergen2023exploratory}. Despite care travel's importance in
advancing gender equality -and equity more broadly-, Mobility of Care
and access to care destinations have been under-examined relative to
employment destinations. This is especially pertinent in accessibility
research that has largely focused on employment points of interest e.g.,
\citep{farberOntarioLineSocioeconomic2019, duarteInfluenceJobAccessibility2023, ryanAccessibilitySpaceTime2023}.

@@

\section{Data}\label{data}

@@

This work focuses on Hamilton, Ontario, a mid-sized city on the shore of
Lake Ontario. Hamilton has a heterogenous land-use, with a populated and
dense urban core, surrounded by suburban development, which is itself
surrounded by rural communities. The Niagara Escarpment runs through
Hamilton, and results in a city with two key elevations: a more dense
lower city that contains the downtown core and the elevated suburban
development referred to as `the Mountain'. In this work, we analyse the
residential parcel centroids, 143,882 locations. We aggregated the
points at the level of Canadian Census Dissemination Area (DA) along
with the population and population per parcel plots in
Figure~\ref{fig-Fig1}.

@@

\begin{longtable}[c]{|p{0.67in}|p{3.94in}|p{2.09in}}

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.67in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{Care\ category}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{Care\ destination\ types}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.09in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{Sources}}} \\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.67in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{Depedent-centric}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{Schools,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{daycares,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{community}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{centres,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{recreation}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{centres,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{parks,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{senior}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{centres,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{long-term}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{care}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{homes,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{retirement}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{homes:}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{1,265}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{locations}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{are}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{included.}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.09in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{(Hamilton}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{2022a,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{2023,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{2022c,}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{2022d;}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{Ontario}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{2023;}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{Ontario GeoHub}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{2023)}}} \\

>>>>

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{unicode-math}
\usepackage{hyperref}
\def\tightlist{}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\floatplacement{figure}{H}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Towards completely caring 15-minute neighbourhoods},
  pdfauthor={Anastasia Soukhov; Léa Ravensbergen; Lucía Mejía Dorantes; Antonio Páez},
  pdfkeywords={15-Minute City, Chrono-Urbanism, Accessibility, Mobility
of Care, Inequality, Gender Gap},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    15-Minute City \sep Chrono-Urbanism \sep Accessibility \sep Mobility
of Care \sep Inequality \sep 
    Gender Gap
\end{keyword}
\end{frontmatter}

@@

The ``15-Minute City'' concept has been embraced by global leaders to
promote human-scale neighbourhoods with transport and land-use designs
that support short trips to daily necessities. This paper bridges the
15-Minute City to ``Mobility of Care'', a framework that foregrounds
travel to care destinations, travel done predominately by women. This
focus contrasts the more commonly studied travel to employment and
leisure destinations. While the 15-Minute City concept is flexible
enough to consider all destination types, gendered examinations are
relatively lacking in the literature, and little research to date has
focused explicitly on care destinations. This gap is addressed in this
paper by identifying which areas in the city of Hamilton, Canada are
`caring 15-minute neighbourhoods'. To do so, a database of care
destinations was compiled to estimate the number (using the cumulative
opportunity accessibility measure) and diversity of mix (using the
entropy measure) of care destinations within a 15-minute walk from
residential parcels. Using data-driven machine learning techniques
(Self-Organizing Maps and Decision Trees), neighborhoods were classified
into `caring 15-minute neighbourhood' typologies that are examined
across residential socio-economic profiles. Our results suggest that the
majority of caring 15-minute neighbourhoods are in the urban core, where
more lower-income households reside. In contrast, not caring 15-minute
neighbourhoods in higher-income peripheral areas. Areas that make good
candidates for urban policy intervention are identified and the
implications of enhancing 15-minute walkable caring access are discussed
in relation to gender mainstreaming in transportation planning and
limitations of this work.

Keywords: 15-Minute City; Chrono-Urbanism; Accessibility; Mobility of
Care; Inequality; Gender Gap

@@

An increasing number of human geographers, planners and other
researchers agree that urban structure influences travel, but city
planning falls short in planning for a neutral identity. In contrast,
cities ought to be planned according to the multiple identities of the
inhabitants
\citep{vacchelli_towards_2018, urbandevelopmentviennaGenderMainstreamingUrban2013}.
Researchers have demonstrated how mobility patterns differ according to
gender
\citep{lawWomenTransportNew1999, cresswell_gendered_2008, levy2013travel, little_gender_1994, tronto_toward_1990}.
The causes for this are varied, and related to gendered social norms and
cultural factors that play a role in how, where, with whom, what for,
and how far we move. Women tend to travel shorter distances and more
frequently \citep{roorda_triap_2010, morency_distance_2011}, and conduct
more activities related to care no matter their stage of life
\citep{ilo_care_2018, garciaromanGenderDifferencesTime2022}. Combined,
these findings indicate that the spatial organization of activities has
a different impact according to gender, and therefore the 15-Minute City
concept should not be gender blind.

This work builds a theoretical bridge between the 15-Minute City and
Mobility of Care concepts to answer questions about what destinations
matter and who benefits from proximity planning. The Mobility of Care
term was coined in
\citet{sanchezdemadariagaMobilityCareIntroducing2013}; it refers to all
travel required to sustain the needs of a household, such as grocery
shopping, escorting children, travelling to health appointments, and
running errands. While decades of research have examined types of
household-serving trips (e.g., shopping trips, escorting to school),
\citet{sanchezdemadariagaMobilityCareIntroducing2013} was the first to
consider them all as one category. In doing so, care-related mobility
can be shown to comprise a significant proportion of daily travel,
characterizing approximately 30\% of adults' daily trips
\citep{sanchezdemadariagaMobilityCareIntroducing2013, sanchezdemadariagaMeasuringMobilitiesCare2019, ravensbergen2023exploratory}.
We argue that Mobility of Care is especially relevant to the 15-Minute
City, as care trips are necessary for \emph{all} people and they most
often occur at the local level. Moreover, care trips are of particular
gendered and socio-economic importance, as women, and especially those
within lower income households, complete the majority of care trips
\citep{ravensbergen2023exploratory}. Despite care travel's importance in
advancing gender equality -and equity\footnote{The United Nations
  defines ``gender equality'' as equal rights, responsibilities, and
  opportunities for all genders, regardless of gender at birth
  \citep{unwomenHandbookGenderMainstreaming2022}; they prefer ``gender
  equality,'' as ``equity'' relates to the concept of fairness that are
  usually based on traditions, customs, or cultural beliefs which can
  perpetuate disadvantage. However, ``equity,'' in the broader context
  of social justice, is widely accepted. As defined in the UNICEF
  Glossary of DEI terms, equity is the ``process of being fair to all
  individuals and groups, by addressing present and historical
  inequality in order to work towards equality in outcomes'' and may
  involve temporary special measures to address systemic discrimination
  faced by marginalized groups \citep{unicefAnnexDIVERSITYEQUITY2024}.}
more broadly-, Mobility of Care and access to care destinations have
been under-examined relative to employment destinations. This is
especially pertinent in accessibility research that has largely focused
on employment points of interest e.g.,
\citep{farberOntarioLineSocioeconomic2019, duarteInfluenceJobAccessibility2023, ryanAccessibilitySpaceTime2023}.

@@

\section{Case study and data}\label{case-study-and-data}

@@

This work focuses on Hamilton, Ontario, a mid-sized city on the shore of
Lake Ontario. Hamilton has a heterogenous land-use, with a populated and
dense urban core, surrounded by suburban development, which is itself
surrounded by rural communities. The Niagara Escarpment runs through
Hamilton, and results in a city with two key elevations: a more dense
lower city that contains the downtown core and the elevated suburban
development referred to as `the Mountain'. In this work, we analyse the
residential parcel centroids, 143,882 locations in the city
\citep{Teranet_2021}. We aggregated the points at the level of Canadian
Census Dissemination Area (DA) along with the population and population
per parcel plots in Figure~\ref{fig-Fig1}. The DA is the most spatially
granual level of publicly available Canadian census data. DAs are
created by Statistics Canada for the purpose of the census and each
represent between 400 to 700 people (Q1:442 and Q3:664 from
Figure~\ref{fig-Fig1}).

@@

\begin{longtable}[c]{|p{1.18in}|p{3.54in}|p{1.97in}}

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.18in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\global\setmainfont{Arial}{Care\ category}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.54in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\global\setmainfont{Arial}{Care\ destination\ types}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.97in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\global\setmainfont{Arial}{Sources}}}} \\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.18in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{Depedent-centric}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.54in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{Schools,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{daycares,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{and}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{community}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{centres,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{recreation}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{centres,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{parks,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{senior}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{centres,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{long-term}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{care}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{homes,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{and}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{retirement}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{homes:}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{1,265}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{locations}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{are}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{included.}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.97in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{(Hamilton}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{2022a,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{2023,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{2022c,}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{2022d;}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{Ontario}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{2023;}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{Ontario GeoHub}}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{8}{0}\selectfont{\global\setmainfont{Arial}{2023)}}}} \\
